### 2020-08-02 thesis/thesis.tex
Latexify coinduction table

%%%%% WLASNE DODATKOWE PAKIETY
% \usepackage{graphicx,listings,tikz}
\usepackage{syntax}
\usepackage{mathalfa}
\usepackage{textcomp}
\usepackage{stmaryrd}
\usepackage{tikz-cd}
% Not sure if necessary
\usepackage[utf8]{inputenc}
\usepackage{rotchiffre}

@@

    \begin{center}
    \begin{tikzcd}[row sep=huge, column sep=large]
        {|M|}^k \arrow[rr, '\phi', bend right] \arrow[rr, '\rrbracket{} X|l', bend left] &  & {|M|}
    \end{tikzcd}
    \end{center}

@@

    \begin{center}
    \begin{tikzcd}
    A \arrow[rd] \arrow[r, '\phi'] & B \\
    & C
    \end{tikzcd}
    \end{center}

@@

    \end{center}
    \\
    together with an universal arrow $ \eta_{A} : A \longrightarrow A^{\#} $.
    Universality means that for every algebra $ \beta : F B \longrightarrow B $
    and every morphism $ f : A \longrightarrow B $ in $ \mathcal{C}$, there
    exists a unique homomorphism $ \overline{f} : A^{\#} \longrightarrow B $
    extending f, i.e.\ a unique morphism of $ \mathcal{C}$ for which the diagram
    below commutes:

@@

    TODO rewrite into latex-table \\

    | feature             | induction            | coinduction          |

    |---------------------|----------------------|----------------------|

    | basic activity      | construction         | deconstruction       |

    | derived activity    | deconstruction       | construction         |

    | functions shape     | inductive domain     | coinductive codomain |

    | (co) recursive calls| shrinks the argument | grows the result     |

    | functions feature   | terminating          | productive           |

    | evaluation          | possibly eager       | necessarily lazy     |

>>>>

%%%%% WLASNE DODATKOWE PAKIETY
% \usepackage{graphicx,listings,tikz}
\usepackage{syntax}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{mathalfa}
\usepackage{csquotes}
\usepackage{textcomp}
\usepackage{stmaryrd}
\usepackage{tikz-cd}
% Not sure if necessary
\usepackage[utf8]{inputenc}
\usepackage{rotchiffre}

@@

    \begin{center}
    % \begin{tikzcd}[row sep=huge, column sep=large]
    %     {|M|}^k \arrow[rr, '\phi', bend right] \arrow[rr, '\rrbracket{} X|l', bend left] &  & {|M|}
    % \end{tikzcd}
    \end{center}

@@

    \begin{center}
    % \begin{tikzcd}
    % A \arrow[rd] \arrow[r, '\phi'] & B \\
    % & C
    % \end{tikzcd}
    \end{center}

@@

    \end{center}
    together with an universal arrow $ \eta_{A} : A \longrightarrow A^{\#} $.
    Universality means that for every algebra $ \beta : F B \longrightarrow B $
    and every morphism $ f : A \longrightarrow B $ in $ \mathcal{C}$, there
    exists a unique homomorphism $ \overline{f} : A^{\#} \longrightarrow B $
    extending f, i.e.\ a unique morphism of $ \mathcal{C}$ for which the diagram
    below commutes:

@@

    \begin{center}
    \begin{tabular}{lcc}
    \toprule

    \textbf{feature}             & \textbf{induction}            & \textbf{coinduction}          \\
    \midrule

    basic activity      & construction          & deconstruction \\
    \midrule

    derived activity    & deconstruction       & construction         \\
    \midrule

    functions shape     & inductive domain     & coinductive codomain \\
    \midrule

    (co) recursive calls& shrinks the argument & grows the result     \\
    \midrule

    functions feature   & terminating          & productive           \\
    \midrule

    evaluation          & possibly eager       & necessarily lazy     \\
    \bottomrule

    \end{tabular}
    \end{center}
